EpiCompare: A tidy \proglang{R} package for comparing and assessing epidemics and epidimology models

### 2020-04-05 jss/jss-article-rnw/article.Rnw
jss minor updates

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
@

@@

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A Short Demo Article: Regression Models for Count Data in \proglang{R}}
\Plaintitle{A Short Demo Article: Regression Models for Count Data in R}
\Shorttitle{A Short Demo Article in \proglang{R}}

@@

\bibliography{refs}

>>>>

%% For Sweave-based articles about R packages:
%% need no \usepackage{Sweave}
\SweaveOpts{engine=R, eps=FALSE, keep.source = TRUE}
<<preliminaries, echo=FALSE, results=hide>>=
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
devtools::load_all()
@

@@

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{EpiCompare: A tidy \proglang{R} package for comparing and assessing epidemics and epidimology models}
\Plaintitle{EpiCompare: A tidy R package for comparing and assessing epidemics and epidimology models}
\Shorttitle{EpiCompare: an \proglang{R} package for comparing and assessing epidemics and models}

@@

\bibliography{EpiCompare}

### 2020-04-05 jss/jss-article-rnw/article.tex
jss minor updates

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Shannon K. Gallagher\\Biostatistics Research Branch \\ National Institute of Allergy and Infectious Diseases
   \AND Benjamin LeRoy\\Department of Statistics \& Data Science\\ Carnegie Mellon University}

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{A Short Demo Article: Regression Models for Count Data in \proglang{R}}
\Plaintitle{A Short Demo Article: Regression Models for Count Data in R}
\Shorttitle{A Short Demo Article in \proglang{R}}

>>>>

%% - \author{} with primary affiliation
%% - \Plainauthor{} without affiliations
%% - Separate authors by \And or \AND (in \author) or by comma (in \Plainauthor).
%% - \AND starts a new line, \And does not.
\author{Shannon K. Gallagher\\
        Biostatistics Research Branch \\ 
        National Institute of Allergy and Infectious Diseases
   \AND Benjamin LeRoy\\
        Department of Statistics \& Data Science\\ 
        Carnegie Mellon University}

%% - \title{} in title case
%% - \Plaintitle{} without LaTeX markup (if any)
%% - \Shorttitle{} with LaTeX markup (if any), used as running title
\title{EpiCompare: A tidy \proglang{R} package for comparing and assessing epidemics and epidimology models}
\Plaintitle{EpiCompare: A tidy R package for comparing and assessing epidemics and epidimology models}
\Shorttitle{EpiCompare: an \proglang{R} package for comparing and assessing epidemics and models}
